Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-03 paper/paper.tex
use xelatex is possible

\subsection{Semantics}
We now give  a small-step semantics for our  language.
We first specify the domains used by the semantics:
\[
\begin{array}{rlcl@{\hspace{0.5em}}l}
\rho: & \mathit{Env} &=&\mathit{Var} \rightarrow \mathit{Loc} &
\mbox{-- Environment} \\
v:   & \mathit{Val} &=& \mathbb{N} + \{\NIL\} + \mathit{Data \times
  Data}& \mbox{-- Values}\\
c:   & \mathit{Clo} &=& \mathit{(Exp \times Env)}& \mbox{--
  Closures}\\
d: & \mathit{Data} &=&\mathit{Val} + \mathit{Clo} & \mbox{-- Values \&
  Closures} \\
\heap: & \mathit{Heap} & =&\mathit{Loc} \rightarrow Data & \mbox{--
Heap}
\end{array}
\]

>>>>

\subsection{Semantics}
We now give  a small-step semantics for our  language.
We first specify the domains used by the semantics:
\[
\begin{array}{@{}r@{\ }l@{\ \ }c@{\ \ }l@{\hspace{0.5em}}l}
\rho: & \mathit{Env} &=&\mathit{Var} \rightarrow \mathit{Loc} & \mbox{-- Environment} \\
v:   & \mathit{Val} &=& \mathbb{N} + \{\NIL\} + \mathit{Data \times Data}& \mbox{-- Values}\\
c:   & \mathit{Clo} &=& \mathit{(Exp \times Env)}& \mbox{-- Closures}\\
d: & \mathit{Data} &=&\mathit{Val} + \mathit{Clo} & \mbox{-- Values \& Closures} \\
\heap: & \mathit{Heap} & =&\mathit{Loc} \rightarrow Data & \mbox{-- Heap}
\end{array}
\]
